A Data-Driven Framework for Neural Field Modelling

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
added to discussion

\section{Future Work}

@@

\section{Acknowledgments}
Dean Freestone would like to thank Dr. Mark van Rossum for hosting him while visiting the University of Edinburgh where this work was undertaken and Dr. Matthias Hennig for useful discussions and feedback. Parham Aram would also like to thank Andrew Hills for useful discussions and assistance with code and the generation of figures.

>>>>

@@

\section{Conclusion}
This paper has made a contribution to bridging the gap between experimental and theoretical neuroscience by developing a systematic methodology. \dean{Please add to this.} Novel aspects of this work include a model reduction procedure such that a finite-dimension state-space model constructed...

\section{Acknowledgments}
Dean Freestone would like to thank Dr. Mark van Rossum for hosting him while visiting the University of Edinburgh where this work was undertaken and Dr. Matthias Hennig for useful discussions and feedback. This research was funded in part by the Australian Research Council (Linkage Project LP0560684). The Bionic Ear Institute acknowledges the support it receives from the Victorian State Government through the Operational Infrastructure Support Program. Dean Freestone would like to thank the University of Melbourne's Scholarships Office for the Postgraduate Overseas Research Experience Scholarship and the Harold Mitchell Foundation for a traveling scholarship for supporting this research. Parham Aram would also like to thank Andrew Hills for useful discussions and assistance with code and the generation of figures.
